Ideology and Identity; Machine Learning Application

### 2021-05-13 Paper Markdown.Rmd
Reoriented directories

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning=FALSE,cache=T,fig.align = "center")
library(tidyverse)
library(scales)
library(igraph)
library(rpart)
library(rpart.plot)
library(rsample)
library(stargazer)
library(gamlr)
library(randomForest)
library(caret)
library(kableExtra)
library(modelr)
library(plm)

source("Scripts/load and first clean.R")
```

#### Introduction

@@

#### Ideological Variable Construction

@@

#### Data Limitations

@@

```{r}
stargazer(reg1,reg2,reg3, title="Regression Results",
align=TRUE, dep.var.labels=c("Position","Extremity","Consistency"),summary.stat = c("n"),type = "html",single.row = T,no.space = T,omit = c("STATE"),summary = T)
```

@@

reg3_step <- step(reg3,scope = ~ (age + agesq + hisp+ own_home+ married+ class_conscious+ discuss+ money_stocks +college +black+ female+ protestant + catholic + inc_firstthird +inc_upperthird +lgbt +middleclass +knowl)^2+.,direction = "both",trace = -10000,steps = 30)
```

```{r rsq-table}
sum_st_r1 <- summary(reg1_step)
sum_st_r2 <- summary(reg2_step)
sum_st_r3 <- summary(reg3_step)
rsq[3,] <- c(sum_st_r1$r.squared,sum_st_r2$r.squared,sum_st_r3$r.squared)
rsq %>% kbl() %>% kable_minimal()
rsq
```

@@

Finally, comparing $R^2$ across each of these models, we see the step regression essentially splits the difference in terms of model fit. The trade-off is strict econometric rigor at the benefit of uncovering identity interactions driving ideological position and structure in the electorate.

#### Discussion

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning=FALSE,fig.align = "center")
library(tidyverse)
library(scales)
library(igraph)
library(rpart)
library(rpart.plot)
library(rsample)
library(stargazer)
library(gamlr)
library(randomForest)
library(caret)
library(kableExtra)
library(modelr)
library(plm)

srv_ideo <- read.csv("DataTurn/srv_ideo.csv")
srv_use <- read.csv("DataTurn/srv_use.csv")

# For reproduction from scratch using ANES data
#source("Scripts/load and first clean.R")
```
### Abstract

In the political science and public opinion literature, the standard OLS method for estimating and predicting effects is in conflict with the highly interconnected nature of identity and ideology. In this paper I attempt two methods for incorporating these methods; regression tree and step regression. Though the success of these methods are small, they each yield results not picked up by OLS. Both have increased predictive power over OLS and yield variable combinations which could not have been constructed a priori.

### Introduction

@@

\newpage

### Methods

#### Data

#### Theory and Variable Construction

@@

#### Models

This study uses three model types to predict ideology from demographic characteristics at different levels of simplicity to demonstrate the effectiveness of machine learning models in dealing with public opinion study.

1. OLS - the gold-standard method for generating academically useable results. This method generates clean estimates of coefficients but lacks the hierarchical and highly-interacted structure characteristic of ideology formation as highlighted in the literature.

2. Regression Trees - Inherently accommodate hierarchy and interactions, but lack clear coefficients and statistical validation measures.

3. Step regressions - Can incorporate interactions like the tree regression, but are suceptible to misspecification of models.

\newpage

### Results

#### OLS

@@

```{r}
stargazer(reg1,reg2,reg3, title="Regression Results",
align=TRUE, dep.var.labels=c("Position","Extremity","Consistency"),summary.stat = c("n"),type = "text",single.row = T,no.space = T,omit = c("STATE"),summary = T) 
```

@@

reg3_step <- step(reg3,scope = ~ (age + agesq + hisp+ own_home+ married+ class_conscious+ discuss+ money_stocks +college +black+ female+ protestant + catholic + inc_firstthird +inc_upperthird +lgbt +middleclass +knowl)^2+.,direction = "both",trace = -10000,steps = 30)

sum_st_r1 <- summary(reg1_step)
sum_st_r2 <- summary(reg2_step)
sum_st_r3 <- summary(reg3_step)
```

@@

```{r}
rsq[3,] <- c(sum_st_r1$r.squared,sum_st_r2$r.squared,sum_st_r3$r.squared)
rsq %>% kbl(caption = "R-Squared Values for each regression", table.attr = "style='width:30%;'") %>% kable_minimal()
```

Finally, comparing $R^2$ across each of these models, we see the step regression does strictly better than OLS, which is expected due to the nature of adding terms to a regression. Interestingly, it also outperforms the tree models in the case of the "consistency" variable. This implies the hierarchical structure of a tree model may actually be less explanatory than the additive linear structure of a regression.

The step model slightly outperforms OLS to a degree where the actual "fit" of the model may not be much better. However, from the step regression coefficients model, we see the process of algorithmically selecting interaciton terms isolated effects not immediately present in the first OLS model. Looking at the Extremity variable, the class and income position affected the predited Extremity of those who often discuss politics, for example.

\newpage

### Conclusion
